Seminar:\\ Quantitative Methoden

### 2024-02-14 draft2.tex
Update

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[ht]
    \caption{Descriptive Statistics}
    \begin{tabularx}{\textwidth}{lXXXXX}
    \hline
                          & Mean   & Std.   & Min & Max & No. obs. \\ \hline
    Employed              & 0.133  & 0.339  & 0   & 1   & 40,295   \\
    Hours worked per week & 5.444  & 14.376 & 0   & 97  & 40,295   \\
    Age                   & 30.681 & 5.829  & 18  & 55  & 40,295   \\
    Married               & 0.976  & 0.155  & 0   & 1   & 40,295   \\
    More than 1 child     & 0.811  & 0.391  & 0   & 1   & 40,295   \\
    First-born boy        & 0.517  & 0.500  & 0   & 1   & 40,295   \\
    Citizen               & 0.943  & 0.231  & 0   & 1   & 40,295   \\
    Number of children    & 3.019  & 1.563  & 1   & 9   & 40,295   \\ \hline
    \end{tabularx}%

@@

Table 1 shows the descriptive statistics for all the variables we used in our analysis. We have 40,305 mothers in our sample.
Noticeable values in the table are that only 13.5\% of mothers are working and accordingly the average hours worked per mother is only 5.
The maximum working hours might seem high,
but since only 1\% of employed mothers work more than 70 hours and there are reports of sweatshops in Jordan with up to 100h worked per week (Greenhouse and Barbaro, 2006) we deemed it plausible.
It is worth to note here, that the working hours per week, only looking at working mothers, is 40.2.
This suggests that part time work is almost non-existent in Jordan, in our sample less than 4\% of working mothers work less that 30 hours per week.
This lack of part time work can partially be of an explanation of the low workforce participation of women. 
Additionally, 97.6\% of mothers are married and 81.1\% have more than 1 child.
All of this points to the fact that Jordan is a highly conservative and religious country with strict gender roles.
In our sample 51.7\% of first-born kids are boys, being close to the natural sex ratio. Therefore the key identification assumption that gender of first born boy is random holds.

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[ht]
    \caption{Descriptive Statistics}
    \begin{tabularx}{\textwidth}{lXXXXX}
    \hline
                          & Mean   & Std.   & Min & Max & No. obs. \\ \hline
    Employed              & 0.135  & 0.339  & 0   & 1   & 40,295   \\
    Hours worked per week & 5.444  & 14.376 & 0   & 97  & 40,295   \\
    Age                   & 30.681 & 5.829  & 18  & 55  & 40,295   \\
    Married               & 0.976  & 0.155  & 0   & 1   & 40,295   \\
    More than 1 child     & 0.811  & 0.391  & 0   & 1   & 40,295   \\
    First-born boy        & 0.517  & 0.500  & 0   & 1   & 40,295   \\
    Citizen               & 0.943  & 0.231  & 0   & 1   & 40,295   \\
    Number of children    & 3.019  & 1.563  & 1   & 9   & 40,295   \\ \hline
    \end{tabularx}%

@@

Table 1 shows the descriptive statistics for all the variables we used in our analysis. We have 40,295 mothers in our sample.
Noticeable values in the table are that only 13.5\% of mothers are working and accordingly the average hours worked per mother is only 5.
The maximum working hours might seem high,
but since only 1\% of employed mothers work more than 70 hours and there are reports of sweatshops in Jordan with up to 100h worked per week (Greenhouse and Barbaro, 2006) we deemed it plausible.
It is worth to note here, that the working hours per week, only looking at working mothers, is 40.2.
This suggests that part time work is almost non-existent in Jordan, in our sample less than 4\% of working mothers work less that 30 hours per week.
This lack of part time work can partially be of an explanation of the low workforce participation of women. 
Additionally, 97.6\% of mothers are married and 81.1\% have more than 1 child.
All of this points to the fact that Jordan is a highly conservative and religious country with strict gender roles.
In our sample 51.7\% of first-born kids are boys, being close to the natural sex ratio. Therefore the key identification assumption that gender of first born boy is random holds.
